---
title: "Weight of Fish"
author: "Mya Orozco"
date: "10/31/2024"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```



## Perch

### Length 1
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottom",main="Adjusted R^2")
```

This data frame shows the height and weight variables are the best model.

### Best Models

```{r}
which.max(summary.out$adjr2)
```

This shows that the model two is the best model to express the data when looking at the Adjusted R-squared value.


### Best Two regressor model
```{r}
summary.out$which[2,]
```

The best model would have to be the perch model 2, this data summary shows model 2 which has the Adjusted r-squared value having two variables meaning model 2 is the best two regression model.




## Pike

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

Now for this model the best appears to be all L1, L2, L3, H, and W. But the best two regressor model appears to be the model including L1 and L3.

### Best Models

```{r}
which.max(summary.out$adjr2)
```

The model with 5 variables is the best model.

### Best Two regressor model
Using leaps we were able to focus its power onto the adjusted r-squared value. Then it would give us only the highest of adjusted r-squared values for 1, 2, 3, 4 and 5 variables for pike. Using this kind of leaps it shows that L1 and L3 are the best two regresses for the highest adjusted r-squared value making it the best two regressor model.  


## Roach

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomleft",main="Adjusted R^2")
```

The best model appears to be the model with 2 variables including L3 and W wich means it is also the best two regressor model.

## Best Models

```{r}
which.max(summary.out$adjr2)
```

This shows that the best model is the one with two variables based off of leaps that is targeting the adjusted r-squared value. The two variables in the leap model is L3 and W.

## Best two regressor model

Leaps has shown the model with the highest adjusted r-squared value has two variables which are L3 and W. So the best two regressor model is the model that has L3 and W.

## Final Summary Statements

Using leaps we were able to target the adjusted r-squared value and easily find the best model for a combination of variables from 1 to 5, 5 being the max for our fish data. This allowed for easy comparisons to find the best regression models.



